Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-24 reply_2/cover_letter.tex
[#22] Add discussion of sign error in simulations to cover letter
We should probably mention the fix to Matias. Done :).  Closes #22.
[#13] Add statement about bias correction similarities to cover letter.

>>>>

Regarding referee 1's comments,
\begin{itemize}
\item the referee noticed that the bias and variance of the analytical
  correction is identical to the bootstrap correction. (Up to reported
  values --- they do differ in higher decimal places that were not
  reported.) This led us to examine our theoretical results more
  carefully and ultimately strengthen Theorem 1. Since both of the
  corrections are based on the same estimated 2nd order polynomial,
  the bootstrap and analytical corrections are not just asymptotically
  equivalent; they are equivalent up to simulation error.
\item We have also clarified the wording issues addressed in comment 2
  and explicitly addressed this coincidence.
\end{itemize}
Regarding referee 2's comments.
\begin{itemize}
\item (placeholder)
\end{itemize}
We have also made the small notational changes and new definitions
the referees requested.

In addition, we discovered a small error in the simulation results ---
instead of reporting each estimator's bias, we reported the negative
bias. Since the values were close to zero, this does not have a
substantive effect on the results but we have, of course, fixed the
tables.
